The shape of dark matter halos in the AURIGA simulations

### 2019-07-08 Document/paper.tex
Spericity study

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_DM.png}
 \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_MHD.png}
\end{center}
\caption{Axial ratios for the 30 halos in the Level 3 DM simulations
  on the left and MHD simulations on the right.
   Each dot represents the shape characterization of each halo at the
   2 times the virial radius and a  1/16 fraction of the virial radius
   differentiated by color. 
   Errorbar shows median and errors for each sampled radii. 
   Conclusion: DM halos are rounder on the outskirts {\bf Esto necesita
  correccion. Debe ser a R1/16 y R (no 2R!)}}
  \label{fig:triax_DM_MHD}
\end{figure*}

@@

Figure  \ref{fig:Star_Density_effect} shows the
{\bf que es es lo que muestra esta grafica? falta las unidades de la
  densidad. y el eje vertical que es? es un cambio absoluto? fraccional?}

@@

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Lvl_4_Triax_Plane_DM.png}
 \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Lvl_4_Triax_Plane_MHD.png}
\end{center}
\caption{Axial ratios for the 30 halos in the Level 3 DM simulations
  on the left and MHD simulations on the right.
   Each dot represents the shape characterization of each halo at the virial radius and a  1/8 fraction of the virial radius
   differentiated by color. 
   Errorbar shows median and errors for each sampled radii. 
   Conclusion: DM halos are rounder on the outskirts {\bf Esto necesita
  correccion. Debe ser a R1/16 y R (no 2R!) Corregido!}}
  \label{fig:triax_DM_MHD}
\end{figure*}

@@

@@

  We measured the sphericity of a halo shape defined as the distance 
  from the point that characterizes the shape in the triaxiality plane
  to the point $(q=1,s=1)$, which represents a perfect sphere. Taking this 
  as our metric of interest, the sphericity question becomes a search for
  important variables and tendencies that affect this quantity. For this case,
  given the small sample of 30 halos, we chose to study this problem with different 
  3 methods to account for the lacking statistical consistency. We analyzed the effect
  of the Star disk Radius, Baryonic fraction, Gas density, BH density, Gas Radius and
  Star density.\\

  We started with a simple linear Lasso regression to force a classification of 
  important variables. Then, we converted this problem in a binary classification problem
  by partitioning the samples in two balanced groups according to the studied metric which was then fitted using Random forest.
  Finally, we concluded this analysis with an MCMC sampling of the likelyhood of a linear model
  with varying slope and intercept parameters.\\

  The results of each method are presented below:

  \begin{table}
\setlength{\tabcolsep}{3pt}
\begin{center}
\begin{tabular}{l|ccc}
 Variable/Method& Lasso& Random Forest & MCMC \\
 & (slope) & (feature importance)&(signal-to noise)\\
\hline 
Star disk Radius &$-0.168 (1)$&$23\% (2)$&$-0.140$  (3)\\[0.1cm]
Gas Radius&$0.081 (5)$&$12.6\% (5)$&$0.217 (1)$\\[0.1cm] 
Star Density &$-0.064 (6)$&$15.2\% (4)$&$-0.102 (6)$\\[0.1cm]
BH Density&$0.084 (4)$&$16.1\% (3)$&$0.108 (5)$\\[0.1cm] 
Gas Density &$0.097 (3)$&$28.4 \%(1)$&$0.202 (2)$\\[0.1cm] 
Baryonic fraction &$-0.167 (2)$&$4\% (6)$&$/0.146 (4)$\\[0.1cm]  
\end{tabular}
\end{center}
\caption{Results of variable importance of the three methods used to analyse
		 the effect of baryons on the rounding effect of halos. Each method has a different
		 metric for the variable importance and are not comparable but in rankings}  
\label{table:sphericity}
\end{table} 
  \begin{figure*}
\centering
{\includegraphics[width=0.6\textwidth]{./pics/Sphericity/Sphericity_signal_to_noise.png}}
\caption{Distribution of likelihood for different values of the linear parameters. This gives us an idea of the consistency of the fit } \label{fig:sphericity}
\end{figure*}
